---
title: Radiant -- Business analytics using R and Shiny
---

***

```{r echo = FALSE}
 rv <- R.Version()
 rv <- paste(rv$major, rv$minor, sep = ".")
```

## How to install Radiant

Radiant is a platform-independent browser-based interface for business analytics in [R](http://www.r-project.org/), based on the [Shiny](http://www.rstudio.com/shiny/) package. Developed by <a href="http://rady.ucsd.edu/faculty/directory/nijs/" target="\_blank">Vincent Nijs</a>. Please use the issue tracker on GitHub to suggest enhancements or report problems: <a href="https://github.com/radiant-rstats/radiant/issues" _target="_blank">https://github.com/radiant-rstats/radiant/issues</a>. For other questions and comments please use radiant@rady.ucsd.edu.

> **Note:** User profiles (or usernames or logins) containing non-ASCII characters will likely cause problems during installation. To address this issue please use a profile name (login) that contains ASCII (A-E, a-e) letters only. For example, c:\\users\\myprofilename

#### 1. Install R for your system

For mac go to <a href="https://cran.rstudio.com/bin/macosx/" target="_blank">https://cran.rstudio.com/bin/macosx/</a>

For windows you can get the latest release here: <a href="https://cran.rstudio.com/bin/windows/base/release.htm" target="_blank">https://cran.rstudio.com/bin/windows/base/release.htm</a>

> **Important:** Windows users **must** install R in directory C:\\R\\R-`r rv`

On Mac you can accept all the defaults. Installing R should create 2 shortcuts on your Desktop. Because we will be using Rstudio to start Radiant you can delete these shortcuts after completing step 6 below.

> To automate steps 2-5 open R and copy-and-paste the command below and accept all default settings:

```r
source("https://raw.githubusercontent.com/radiant-rstats/minicran/gh-pages/install.R")
```

#### 2. Install Rstudio

Get the latest release of Rstudio for your system from:

<a href="https://www.rstudio.com/products/rstudio/download/" target="_blank">https://www.rstudio.com/products/rstudio/download/</a>

Install Rstudio and accept all default settings. Make sure to put a shortcut to Rstudio on your Desktop.

Although not required, I recommend that Windows users install <a href="https://cran.rstudio.com/bin/windows/Rtools/Rtools33.exe" target="_blank">Rtools</a>.

#### 3. Use a modern browser

For example, [Chrome](https://www.google.com/intl/en/chrome/browser/desktop/) or Safari. Internet Explorer (version 11 or higher) should work as well. Chrome, however, is the recommended browser.

#### 4. Install Tex 

To generate PDF reports in Radiant you will need LaTex installed. For Mac download and install <a href="http://tug.org/cgi-bin/mactex-download/MacTeX.pkg">MacTex</a>. For Windows download and install <a href="http://mirrors.ctan.org/systems/win32/miktex/setup/basic-miktex-2.9.5997-x64.exe">MikTex</a>.

#### 5. Install Radiant

To install Radiant open Rstudio and copy-and-paste the command below into the **Console** window on the bottom left of the application. Then press return. R(studio) will now install Radiant and several dependencies. This may take a few minutes depending on the speed of your internet connection.

> **Note:** On Windows you may need to start Rstudio by right-clicking on the desktop shortcut and choosing `run as administrator`.

```r
install.packages("radiant", repos = "https://radiant-rstats.github.io/minicran/", type = "binary")
```

> **Important:** If you use Windows and are asked where to install Radiant (i.e., "Would you like to use a personal library instead?") you most likely did **not** install R in directory C:\\R\\R-`r rv` as stated above. You should uninstall and reinstall R in the suggested directory before proceeding.

#### 6. Starting Radiant

When you open Rstudio (version 0.99.893 or later) by double-clicking the icon on your Desktop you can start and update Radiant through the `Addins` menu at the top of the screen. Note that when you first install Radiant you must use the `install.packages` command shown above.

When Radiant starts you will see data on diamond prices. To close the application click the <i title='Power off' class='fa fa-power-off'></i> icon in the navigation bar and then click `Stop`. The Radiant process will stop and the browser window will close (Chrome) or gray-out. If you get stuck, take a look at the `Installing Radiant` video:

<iframe width="640" height="375" src="https://www.youtube.com/embed/XLR9cquIMAg" frameborder="0" allowfullscreen></iframe>

## Documentation

Documentation and tutorials for each of the apps are available at <http://radiant-rstats.github.io/docs/> and in the Radiant web interface (the <i title='Help' class='fa fa-edit'></i> icons on each page and the <i title='Help' class='fa fa-question-circle'></i> icon in the navigation bar).

Want more help getting started? Watch the tutorials on the [documentation site](http://radiant-rstats.github.io/docs/tutorials.html).

## Trouble shooting

As mentioned above, Windows users may need to start Rstudio by right-clicking on the Rstudio desktop shortcut and choosing `run as administrator`.

On Windows, if you see a message such as "Warning: unable to move temporary installation 'C:\Users\yourname\Documents\R\win-library\3.x\file54ad976f6\shinyAce' to 'C:\Users\yourname\Documents\R\win-library\3.x\shinyAce'"
you should reinstall R into C:\\R\\R-`r rv` as mentioned above. You should also remove the Documents\\R folder from your computer

On rare occasions R(studio) may complain that a package is not yet installed. If so, install the package mentioned using the command below but replace 'package-that-is-not-yet-installed' with the package name mentioned in the error message

```{r eval = FALSE}
install.packages("package-that-is-not-yet-installed", repos = "https://radiant-rstats.github.io/minicran/", type = "binary")
```

## Reporting issues

Rady students can report any issues they might have with Radiant on Piazza. Otherwise, please use the GitHub issue tracker at <a href="https://github.com/radiant-rstats/radiant/issues" target="_blank">github.com/radiant-rstats/radiant/issues</a> if you have any problems with Radiant.

